A Higher-Order Approach to Explicit Contexts in LF

### 2015-03-08 paper/paper.tex
repair contradiction in terms

\section{Encoding Functional Hypothetico-General Judgement}
Henceforth I shall use the term ``functional sequent judgement'' to mean a
hypothetico-general judgement which also requires functionality. First, before
we get to the functional sequent judgement, we will need the concept of an
``general categorical judgement''; this is a judgement which has variables from
a telescope free in it.

>>>>

\section{Encoding Functional Hypothetico-General Judgement}
Henceforth I shall use the term ``functional sequent judgement'' to mean a
hypothetico-general judgement which also requires functionality. First, before
we get to the full sequent judgement, we will need the concept of an
``general judgement''; this is a judgement which has variables from
a telescope free in it.
